Internal models of type theory

### 2013-10-26 article-models-eg.tex
Started description of the model of equifibered diagrams

\subsection{The Sierpinsky model}.
In the Sierpinsky model, contexts are interpreted by dependent types $A\to\type$.

@@

>>>>

@@

\subsection{The model of equifibered families of graphs}
We describe the model $\equifib$ of equifibered families of graphs. The contexts
are still the graphs. However, the types of $\equifib$ are not just the
families of graphs, but the equifibered families of graphs. This will have
far-reaching consequences for the rest of the structure of the model. As an
example, a morphism of graphs will no longer be a pair consisting of a map of
vertices and a map of edges.

\begin{defn}
Let $\Gamma$ be a graph. A type in context $\Gamma$ is a triple 
$\pairr{A_0,A_1,A_2}$ consisting of
\begin{align*}
A_0 & : \Gamma_0\to\type\\
A_1 & : \prd*{i,j:\Gamma_0}{q:\Gamma_1(i,j)}A_0(i)\to A_0(j)\\
A_2 & : \prd*{i,j:\Gamma_0}{q:\Gamma_1(i,j)}\isequiv{A_1(q)}
\end{align*}
A type in context $\Gamma$ is also called an equifibered family over $\Gamma$.
\end{defn}

\begin{defn}
Let $\Gamma$ be a graph. A term of $\Gamma$ is a term of $\Gamma_0$.
\end{defn}

\begin{defn}
Let $A$ be an equifibered family over $\Gamma$. A term $x$ of $A$ is a pair
$\pairr{x_0,x_1}$ consisting of
\begin{align*}
x_0 & : \prd{i:\Gamma_0}A_0(i)\\
x_1 & : \prd*{i,j:\Gamma_0}{q:\Gamma_1(i,j)}\id{A_1(q,x_0(i))}{x_0(j)}
\end{align*}
\end{defn}

\begin{defn}
Suppose that $A$ is an equifibered family over $\Gamma$. We define the graph
$\ctxext{\Gamma}{A}$ to consist of
\begin{align*}
\ctxext{\Gamma}{A}_0 & \defeq\sm{i:\Gamma_0}A_0(i)\\
\ctxext{\Gamma}{A}_1(\pairr{i,x},\pairr{j,y}) & \defeq \sm{q:\Gamma_1(i,j)}\id{A_1(q,x)}{y}.
\end{align*}
\end{defn}

\begin{defn}
Suppose $\Gamma$ and $\Delta$ are graphs. We define the equifibered family
$\ctxwk{\Gamma}{\Delta}$ over $\Gamma$ to consist of
\begin{align*}
\ctxwk{\Gamma}{\Delta}_0(i) & \defeq \Delta\\
\ctxwk{\Gamma}{\Delta}_1(q) & \defeq \idfunc[\Delta]\\
\ctxwk{\Gamma}{\Delta}_2(q) & \defeq \nameless.
\end{align*}
The proof $\ctxwk{\Gamma}{\Delta}_2(q)$ that $\ctxwk{\Gamma}{\Delta}_1(q)$ is an
equivalence is the canonical proof that $\idfunc[\Delta]$ is an equivalence, for
which we don't have a name.
\end{defn}

\begin{defn}
Suppose $A$ and $B$ are equifibered families over $\Gamma$. We define the equifibered
diagram $\ctxwk{A}{B}$ over $\ctxext{\Gamma}{A}$ to consist of
\begin{align*}
\ctxwk{A}{B}_0(\pairr{i,x}) & \defeq B_0(i)\\
\ctxwk{A}{B}_1(\pairr{q,\alpha}) & \defeq B_1(q)\\
\ctxwk{A}{B}_2(\pairr{q,\alpha}) & \defeq B_2(q).
\end{align*}
\end{defn}

\begin{defn}
Suppose $A$ is an equifibered family over $\Gamma$ with $x:A$ and that $P$ is an equifibered
family over $\ctxext{\Gamma}{A}$. Then we define the equifibered family $\subst{x}{P}$
over $\Gamma$ to consist of
\begin{align*}
\pts{\subst{x}{P}}(i) & \defeq \pts{P}(\pts{x}(i))\\
\edg{\subst{x}{P}}(q,u) & \defeq \edg{P}(\pairr{q,\edg{x}(q)},u)\\
\subst{x}{P}_2(q) & \defeq P_2(\pairr{q,\edg{x}(q)}).
\end{align*}
\end{defn}

\begin{defn}
Suppose that $A$ is an equifibered family over $\Gamma$ and that $P$ is an
equifibered family over $\ctxext{\Gamma}{A}$. Then we define the equifibered
family $\msm{A}{P}$ over $\Gamma$ by
\begin{align*}
\pts{\msm{A}{P}}(i) & \defeq \sm{x:\pts{A}(i)}\pts{P}(x)\\
\edg{\msm{A}{P}}(q,\pairr{x,u}) & \defeq \pairr{\edg{A}(q,x),\edg{P}(\pairr{q,\refl{\edg{A}(q,x)}},u)}\\
\msm{A}{P}_2(q,\pairr{x,u}) & \defeq \nameless.
\end{align*}
\end{defn}
